---
title: "R Notebook"
output:
  word_document: default
  pdf_document: default
  html_document:
    self_contained: no
---

## Introducción

Se instalan los paquetes necesarios

```{r}
# install.packages(c("Rtools ","dplyr",
#                  	"ggplot2",
# 	"gridExtra",
# 	"tidyr",
# 	 "reshape2",
# 	 "RClorBrewer",
#             	"ggrepel"))

```

**Para empezar debe de instalar los siguientes paquetes:**

```{r}
library(dplyr)
library(ggplot2)
library(gridExtra)
library(tidyr)
library(reshape2)
library(RColorBrewer)
library(ggrepel)

```

## Se procede a leer los pokemons

```{r}
df= (read.csv(file.choose(), header=T, encoding = "UTF-8"))
summary(df)
```

```{r}
df = tbl_df(df)
colnames(df)[25] <- "classification" 
df$capture_rate <- as.numeric(df$capture_rate)
head(df)

```

```{r}
df <- select(df, name, classification, hp, weight_kg, 
            height_m, speed, attack, defense,
            sp_attack, sp_defense, type1, type2, 
            abilities, generation,is_legendary, 
            capture_rate)
head(df)
```

```{r}
density_hp <- ggplot(data=df, aes(hp)) + geom_density(col="white",fill="pink", alpha=0.8) + ggtitle("Density Plot of HP")

density_speed <- ggplot(data=df, aes(speed)) + geom_density(col="white", fill="darkorchid", alpha=0.8) + ggtitle("Diagrama densidad de caracteristicas de velocidad")

density_attack <- ggplot(data=df, aes(attack)) + geom_density(col="white", fill="orange", alpha=0.7) + ggtitle("Diagrama densidad de caracteristicas ofensivas")

density_defense <- ggplot(data=df, aes(defense)) + geom_density(col="white", fill="firebrick", alpha=0.7) + ggtitle("Diagrama densidad de caracteristicas defensivas")

density_height <- ggplot(data=df, aes(height_m)) + geom_density(col="white", fill="slateblue1", alpha=0.8) + ggtitle("Diagrama de densidad basado n altura (m) ")

density_weight <- ggplot(data=df, aes(weight_kg)) + geom_density(col="white", fill="mediumturquoise", alpha=0.8) + ggtitle("Diagrama densidad Peso (kg)")

grid.arrange(density_hp, density_speed, density_attack, density_defense, density_height, density_weight, ncol=2)

```

```{r}
type_1_poke <- ggplot(data=df, aes(type1)) + geom_bar(aes(fill=..count..), alpha=0.8) + theme(axis.text.x = element_text(angle = 90, hjust = 0)) + ggtitle("Distribucion basados en Type-1") + coord_flip()
type_2_poke <- ggplot(data=df, aes(type2)) + geom_bar(aes(fill=..count..), alpha=0.8) + theme(axis.text.x = element_text(angle = 90, hjust = 0)) + ggtitle("Distribucion basados en Type-2") + coord_flip()

grid.arrange(type_1_poke, type_2_poke, ncol=2)

```

```{r}
df %>%
filter(is_legendary==1) %>%
ggplot(aes(type1)) + geom_bar(aes(fill= ..count..)) + theme(axis.text.x = element_text(angle=90, hjust=0)) + ggtitle("Numero de Pokemon Legendarios usando Type-1")

```

```{r}
ggplot(data=df, aes(attack, defense)) + geom_point(aes(color=is_legendary), alpha=0.8) + scale_color_gradient(low="darkblue", high="red") + ggtitle("Contraste Caracteristicas de Defensa vs Ataque") + 
  geom_label_repel(data=subset(df,attack > 150 | defense >150 | attack < 25), aes(label=name), 
                   box.padding = 0.35, point.padding = 0.5,
                   segment.color = 'grey50')

```

```{r}
speed_attack_legendary <- ggplot(na.omit(df), aes(attack, speed)) + geom_point(aes(color=is_legendary)) + 
geom_label_repel(data=subset(df, (attack > 170 | attack < 50 & speed >150 | speed < 50) & is_legendary == 1 | speed > 145), aes(label=name), box.padding = 0.35, point.padding = 0.5, segment.color = 'grey50') + 
geom_smooth(method = "lm")

weight_attack_legendary <- ggplot(na.omit(df), aes(attack, weight_kg)) + geom_point(aes(color=is_legendary)) + 
geom_label_repel(data=subset(df, (attack > 170 | attack < 50 | weight_kg > 650) & (is_legendary == 1)), aes(label=name), box.padding = 0.35, point.padding = 0.5, segment.color = 'grey50') + 
geom_smooth(method = "lm")

height_attack_legendary <- ggplot(na.omit(df), aes(attack, height_m)) + geom_point(aes(color=is_legendary)) + 
geom_label_repel(data=subset(df, ((attack > 170 | attack < 50 | height_m > 7.5) & is_legendary == 1) | height_m > 5 & is_legendary == 0), aes(label=name), box.padding = 0.35, point.padding = 0.5, segment.color = 'grey50') + 
geom_smooth(method = "lm")

hp_attack_legendary <- ggplot(na.omit(df), aes(attack, hp)) + geom_point(aes(color=is_legendary)) + 
geom_label_repel(data=subset(df, ((attack > 170 | hp > 190 | attack < 50) & is_legendary == 1) | hp >160), aes(label=name), box.padding = 0.35, point.padding = 0.5, segment.color = 'grey50')  + 
geom_smooth(method = "lm")

# grid.arrange(speed_attack_legendary, weight_attack_legendary, height_attack_legendary, hp_attack_legendary, ncol = 2)
#Velocidad, altura, peso y Hp vs atributo de defensa

speed_attack_legendary
weight_attack_legendary
height_attack_legendary
hp_attack_legendary

```

```{r}
speed_defense_legendary <- ggplot(na.omit(df), aes(defense, speed)) + geom_point(aes(color=is_legendary)) + 
geom_label_repel(data=subset(df, (defense > 130 | defense < 50| speed > 140 | speed < 50) & is_legendary == 1), aes(label=name), box.padding = 0.35, point.padding = 0.5, segment.color = 'grey50') + 
geom_smooth(method = "lm")

weight_defense_legendary <- ggplot(na.omit(df), aes(defense, weight_kg)) + geom_point(aes(color=is_legendary)) + 
geom_label_repel(data=subset(df, (defense > 160 | defense < 50 | weight_kg > 600) & is_legendary == 1), aes(label=name), box.padding = 0.35, point.padding = 0.5, segment.color = 'grey50') + 
geom_smooth(method = "lm")

height_defense_legendary <- ggplot(na.omit(df), aes(defense, height_m)) + geom_point(aes(color=is_legendary)) + 
geom_label_repel(data=subset(df, (defense > 150 | defense < 50 | height_m > 6) & is_legendary == 1 | height_m >5 & is_legendary ==0), aes(label=name), box.padding = 0.35, point.padding = 0.5, segment.color = 'grey50') + 
geom_smooth(method = "lm")

hp_defense_legendary <- ggplot(na.omit(df), aes(defense, hp)) + geom_point(aes(color=is_legendary)) + 
geom_label_repel(data=subset(df, (defense > 150 | defense < 50 | hp > 150) & is_legendary == 1 | hp > 200), aes(label=name), box.padding = 0.35, point.padding = 0.5, segment.color = 'grey50') + 
geom_smooth(method = "lm")

# grid.arrange(speed_defense_legendary, weight_defense_legendary, height_defense_legendary, hp_defense_legendary, ncol = 2)
speed_defense_legendary
weight_defense_legendary
height_defense_legendary
hp_defense_legendary

```

```{r}
box_plot_attr <- select(df, type1, is_legendary, hp, defense, attack, sp_attack, sp_defense, speed)

box_plot_attr_leg <- filter(box_plot_attr, is_legendary == 1)

box_plot_attr_nor <- filter(box_plot_attr, is_legendary == 0)
box_plot_attr_leg_long <- gather(box_plot_attr_leg, attribute, value, -c(type1, is_legendary))

box_plot_attr_nor_long <- gather(box_plot_attr_nor, attribute, value, -c(type1, is_legendary))

bp_leg <- ggplot(data = box_plot_attr_leg_long, aes(attribute, value)) + geom_boxplot(fill="green4") + ggtitle("Pokemon Legendario")

bp_nor <- ggplot(data = box_plot_attr_nor_long, aes(attribute, value)) + geom_boxplot(fill = "yellow2") + ggtitle("Pokemon Normal")

grid.arrange(bp_leg, bp_nor,ncol=2)

```

```{r}
hmap_attr <- select(df, type1, is_legendary, hp, defense, attack, sp_attack, sp_defense, speed)
hmap_attr_leg <- filter(hmap_attr, is_legendary == 1)
hmap_attr_nor <- filter(hmap_attr, is_legendary == 0)
hmap_attr_leg <- group_by(hmap_attr_leg, type1)
hmap_attr_nor <- group_by(hmap_attr_nor, type1)
hmap_attr_leg <- summarise(hmap_attr_leg, hp=median(hp), attack=median(attack), defense=median(defense), sp_attack=median(sp_attack), sp_defense=median(sp_defense), speed=median(speed))

hmap_attr_leg_m <- melt(hmap_attr_leg)
hmap_attr_nor <- summarise(hmap_attr_nor, hp=median(hp), attack=median(attack), defense=median(defense), sp_attack=median(sp_attack), sp_defense=median(sp_defense), speed=median(speed))
hmap_attr_nor_m <- melt(hmap_attr_nor)
hm.palette <- colorRampPalette(rev(brewer.pal(5, 'RdYlBu')), space='Lab')

ggplot(data=hmap_attr_leg_m, aes(type1, variable)) + geom_tile(aes(fill=value)) + ggtitle("Legendary Pokemon: Type1 - Attribute") + scale_fill_gradientn(colours = hm.palette(100)) + theme(axis.text.x = element_text(angle=90, hjust=0)) + coord_equal()

```

```{r}
hm.palette <- colorRampPalette(rev(brewer.pal(5, 'RdYlBu')), space='Lab')

ggplot(data=hmap_attr_nor_m, aes(type1, variable)) + geom_tile(aes(fill=value)) + ggtitle("Non Legendarios Atributo Tipo 1") + scale_fill_gradientn(colours = hm.palette(100)) + theme(axis.text.x = element_text(angle=90, hjust=0)) + coord_equal()

```

```{r}
# Elije los atributos que va a sacar la correlación
hmap_attr <- select(df, type1, is_legendary, hp, defense, attack, sp_attack, sp_defense, speed)

# Filtra por tipo de pokemon legendario y no legendario
hmap_attr_leg <- filter(hmap_attr, is_legendary == 1)
hmap_attr_nor <- filter(hmap_attr, is_legendary == 0)

# Agrupa los datos por tipo... Para que las operaciones se hagan sobre los grupos
hmap_attr_leg <- group_by(hmap_attr_leg, type1)
hmap_attr_nor <- group_by(hmap_attr_nor, type1)

# Se procede a hacer la mediana para cada uno de los grupos
hmap_attr_leg <- summarise(hmap_attr_leg, hp=median(hp), attack=median(attack), defense=median(defense), sp_attack=median(sp_attack), sp_defense=median(sp_defense), speed=median(speed))

hmap_attr_nor <- summarise(hmap_attr_nor, hp=median(hp), attack=median(attack), defense=median(defense), sp_attack=median(sp_attack), sp_defense=median(sp_defense), speed=median(speed))


row.names(hmap_attr_leg) <- hmap_attr_leg$type1 # Qué hace esto

hmap_attr_leg$type1 <- NULL

hmap_attr_leg$is_legendary <- NULL

row.names(hmap_attr_nor) <- hmap_attr_nor$type1

hmap_attr_nor$type1 <- NULL

hmap_attr_nor$is_legendary <- NULL


hmap_attr_leg_cor <- cor(hmap_attr_leg)

hmap_attr_leg_cor_m <- melt(hmap_attr_leg_cor)

hm.palette <- colorRampPalette(rev(brewer.pal(5, 'GnBu')), space='Lab')

ggplot(data=hmap_attr_leg_cor_m, aes(Var1, Var2))  +theme_minimal()+ geom_tile(aes(fill=value)) + ggtitle("Correlación de Atributos - Legendarios") + scale_fill_gradientn(colours = hm.palette(100))



cor_pval <- dcast(hmap_attr_leg_cor_m, Var1~Var2)[, -1]
# Set to NA upper triangle excluding diagonal
cor_pval[upper.tri(cor_pval, diag=F)] <- NA 

cor_pval_col <- melt(cor_pval)

hmap_attr_leg_cor_m$value2 <- cor_pval_col$value
hmap_attr_leg_cor_m



ggplot(data=hmap_attr_leg_cor_m, aes(x = Var1, y = Var2, fill=value2)) + geom_raster() +  ggtitle("Correlación de Atributos - Legendarios") + scale_fill_gradientn(colours = hm.palette(100), na.value = "white") + theme_minimal()
  
```

```{r}
hmap_attr_nor_cor <- cor(hmap_attr_nor)
hmap_attr_nor_cor_m <- melt(hmap_attr_nor_cor)

hm.palette <- colorRampPalette(rev(brewer.pal(5, 'GnBu')), space='Lab')

ggplot(data=hmap_attr_nor_cor_m, aes(Var1, Var2)) + geom_tile(aes(fill=value)) + ggtitle("Correlación de Atributos - Noraml") + scale_fill_gradientn(colours = hm.palette(100)) + theme_minimal() 

```

Buscar en:

<https://stackoverflow.com/questions/51697101/how-to-do-a-triangle-heatmap-in-r-using-ggplot2-reshape2-and-hmisc> -\> Se usa theme_minimal

```{r}

df_fight_against <- select(df, type1, against_bug:against_water)

head(df_fight_against)

#Se deben encontrar la mediana de todas las columnas against_type

df_fight_against_g <- group_by(df_fight_against, type1)

df_fight_against_summ <- summarise(df_fight_against_g,
                                   against_bug = median(against_bug),
                                   against_dark = median(against_dark),
                                   against_dragon = median(against_dragon),
                                   against_electric = median(against_electric),
                                   against_fairy = median(against_fairy),
                                   against_fight = median(against_fight),
                                   against_fire = median(against_fire),
                                   against_flying = median(against_flying),
                                   against_ghost = median(against_ghost),
                                   against_grass = median(against_grass),
                                   against_ground = median(against_ground),
                                   against_ice = median(against_ice),
                                   against_normal = median(against_normal),
                                   against_poison = median(against_poison),
                                   against_psychic = median(against_psychic),
                                   against_rock = median(against_rock),
                                   against_steel = median(against_steel),
                                   against_water = median(against_water))

# Ploteamos el heatmap

df_fight_against_long <- melt(df_fight_against_summ)
hm.palette <- colorRampPalette(rev(brewer.pal(9, 'RdYlBu')), space='Lab')

ggplot(data=df_fight_against_long, aes(type1, variable)) + geom_tile(aes(fill=value)) + scale_fill_gradientn(colours = hm.palette(100)) + coord_equal() + 
theme(axis.text.x=element_text(angle=90, hjust=0)) + ggtitle("Efectividad de Diferentes Tipos Pokemon") # Cambiar los títulos por algo más representativos efectividad por resistencia

```

```{r}
#df %>% count(type1, type2)%>% filter(type1=="fire")

df %>% filter(type1=="flying") %>% select(name,against_grass,type1)
df %>% filter(type1=="flying")%>% select(name,against_ice,type1)



df %>% filter(type1=="fire")%>% select(name,against_ice,type1)%>% 
  summarise(median(against_ice))
```

# ERROR 1

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
